Sexual selection improves population fitness: a systematic review and meta-analysis

### 2019-01-16 Response_to_Nature_Comms.Rmd

load(".RData")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Dear Dr. Jones and colleagues,

We appreciate the insightful comments provided by the Associate Editor and reviewers. We have made the suggested changes and clarifications, detailed below. In addition to the revised manuscript and revised supplementary material, we attach a copy of the revised manuscript in which the significant changes and additions have been highlighted.

@@

>*The manuscript presents results of a meta-analysis assessing the effect of sexual selection on population fitness. This topic has been increasingly studied over the past decade or so, and the time seems ripe for a synthesis. The authors have done good job searching the literature – it includes all relevant papers I could remember, and the results should be of interest to a broad range of evolutionary biologists. I cannot expertly judge on state-of-the-art methodology, but I do have several general concerns about how the analyses were performed.*

Many thanks for your time and for you very helpful feedback.

>*Firstly, it seems that several male traits like to be under sexual selection, but not related to population fitness were included. I don’t think this is correct given the question being asked (i.e. whether sexual selection increases population fitness). I think traits which are directly under sexual selection (eg. attractiveness, reproductive success) should not be pooled with traits which may respond to manipulation of sexual selection indirectly (eg. male development time, survival) and can affect population fitness. Distinguishing between both types of trait could actually be revealing – e.g. could expose trade-offs between sexually selected traits and fitness components unrelated to reproductive competition (see eg. Radwan et al. 2015 Evol Biol), a thus potentially explain lower effect of sexual selection on (pooled) male traits than on female traits.*

We appreciate the reviewer's point that distinguishing between traits that are direct targets of sexual selection, versus those that respond more indirectly, could be revealing. For this reason, we present separate meta-analytical measurements for the effects of sexual selection on each of the various fitness components in the supplementary material. This enables the reader to gauge the effect of sexual selection each of the fitness components, e.g. to test whether direct targets of sexual selection (such as attractiveness) respond more strongly to sexual selection than traits such as immunity or longevity with a more indirect link to reproduction.

However, because the subject of our study is population fitness, we classified fitness components according to their relationship to population fitness, rather than their relationship with sexual selection. We took this decision because the relationship between sexual selection and population fitness is contentious, while there is no controversy over how sexual selection should affect traits like attractiveness (almost by definition, individuals born under sexual selection should be more attractive whenever attractiveness is hereditary).

In the revision, we have slightly altered which traits were classified as having a "direct", "indirect", or "ambiguous" relationship with population fitness, in light of the reviewer's feedback (see Table S1 for a breakdown of how all the traits were classified). Because we think that attractiveness is only tenuously linked to population fitness, and we have re-classified its relationship with population fitness as "ambiguous" (as opposed to "indirect" in the original manuscript). Additionally, we have split the trait "Reproductive success" by sex, in light of the fact that male and female fitness are maximised in differenet ways and are likely to have differentially related to population fitness. The revised manuscript and its main figures show that this reclassification had little impact on our main conclusions.

@@

  #Add theme specifying text size, margins, lines etc.
  theme_bw()+

  theme(strip.text.y = element_text(angle = 0, size = 12, margin = margin(t=15, r=15, b=15, l=15)), 
        strip.background = element_rect(colour = NULL,
                                        linetype = "blank",
                                        fill = "gray90"),
        text = element_text(size=13),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.text = element_text(size=12), 
        legend.title=element_text(size=12, 
                                  face = "bold"),
        axis.title.x = element_text(hjust = 0.5, size = 12))

p.meta.male.attract
```

We agree that alone, these 6 effect sizes do not provide strong evidence that the true mean effect size is positive. But given that all but two of the effect sizes are positive, and some of them are very precisely measured, this only-just-significant result does not seem incorrect.

We thought about the reviewer's comment regarding random slopes, and it's not clear what revised model he is proposing. The current model has the following attributes:

- *Effect size* (i.e. the effect of sexual selection treatment on some fitness component) as the response variable, weighted by the associated standard error
- The *type of fitness trait* (e.g. fecundity, lifespan, attractiveness) as a fixed factor or 'moderator vairable'
- The *Study ID* as a random intercept (to model the similarity among effect sizes derived from the same study)
- The *Taxon* as a random intercept (to model the similarity among effect sizes pertaining to the same taxon)

So, is the reviewer proposing to add the fixed factor *type of fitness trait* as a random slope? If we understand correctly, this would allow each different fitness trait to differ in the amount of variance explained by study or taxon. We suspect that such a model would be overly-complex given the structure and size of our dataset, and it is unlikely to provide a statistically significantly better fit than the more parsimonious model that we currently use. Rather few studies measured multiple traits, and there are several taxa in which only one or two trait types have been measured, so there would be many components of the model that could not be estimated.

Alternatively, it is possible that the reviewer meant for us to build a model that allows the response to sexual selection treatment to differ among the fitness traits. In pseudocode, this would look something like `Trait_value ~ Sexual_selection_treatment * Type_of_trait`. However, this would represent a misunderstanding of meta-analysis: we do not analyse the raw trait values from the original studies, but rather collect their effect sizes and combine them to estimate the average effect size for each of the different fitness traits. Our present analysis already allows for the possibility that the response to sexual selection differs between the different types of fitness trait. Apologies in advance if we have missed the point you were making, and thank you for this thought-provoking feedback.

In light of this comment, we have changed our main figure for greater clarity and simplicity (we now group the traits by their relationship to population fitness, as opposed to the numerous individual types of types). Specifically we have changed Figure 1 to a simpler style of forest plot, with the big forest plot that was formerly Figure 1 now moved to the Supplementary Material (Fig. S1).

### 2019-01-22 Manuscripts/Manuscript_MetaAnalysis.Rmd
Changes to manuscript, I2, letter and supp Material

The grand mean for all effect sizes (**direct, indirect and ambiguous**) was positive (REML $\beta$ = 0.24, 95% CIs: 0.055 to 0.43, $p$ = 0.011; Bayesian $\beta$ = 0.25, 95% CIs: -0.0074 to 0.51, $BF_{>0}$ = 35), indicating that sexual selection **on males** typically had a net positive effect on the majority of populations and fitness components so far studied. Moreover, the effect sizes associated with the manipulation of sexual selection varied between different fitness traits. Sexual selection had a beneficial effect on most fitness traits, but varied across the three relationships to fitness \autoref{forest_plot}; \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S6}). **Sexual selection elevated fitness for traits that shared an ambiguous relationship to fitness (REML $\beta$ = 0.21, 95% CIs: 0.058 to 0.093; Bayesian $\beta$ = 0.20, 95% CIs: -0.0016 to	0.39, $BF_{>0}$ = 38, $n$ = 144) and an indirect relationship to fitness (REML $\beta$ = 0.24, 95% CIs: 0.13 to 0.36; Bayesian $\beta$ = 0.24, 95% CIs: 0.033 to 0.43, $BF_{>0}$ = 59, $n$ = 141). Additionally, sexual selection elevated fitness components directly related to fitness, albeit at a lower magnitude (REML $\beta$ = 0.13, 95% CIs: 0.019 to 0.24; Bayesian $\beta$ = 0.13, 95% CIs: -0.079 to 0.31, $BF_{>0}$ = 11, $n$ = 174). An extensive forest plot with predicted effect sizes for each fitness component is presented in Figure S1 and further detailed in model prediction and individual meta-analyses in** \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S8 and S9}. Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.42, 95% CIs: -0.64 to -0.20; Bayesian $\beta$ = -0.43, 95% CIs: -0.70 to -0.15, $BF_{>0}$ = 0.0026; $n$ = 35) and body condition (REML $\beta$ = -1.2, 95% CIs: -1.8 to -0.63; Bayesian $\beta$ = -1.2, 95% CIs: -1.9 to -0.63, $BF_{>0}$ < 0.0001, $n$ = 1).  \phantomsection

@@

The effect size estimates we recovered were highly heterogeneous ($I^2$ = 95.4%, 95% CIs: 93.5-96.8%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208; @Senior_I2_2016]. Most of the observed heterogeneity stemmed from between-study differences ($I^2_{study}$ = 57.9%, 95% CIs: 38.8-76.7%), with variation between fitness components accounting for comparatively less heterogeneity ($I^2_{fitness\:components}$ = 37.2%, 95% CIs: 18.2-57.2%). The effect of taxon varied between REML and Bayesian models: the REML model suggested no effect ($I^2_{taxon}$ = 0), while the Bayesian model **suggested a probable non-zero effect** ($\sigma^2$ = 0.15 [0-0.54]). Variation among taxa is explored further in the ESM (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_to_just_the_higher-quality_data}{Figure S2, Table S11}).  \phantomsection

@@

As in the meta-analysis of trait means, there was high heterogeneity in the estimates of *lnCVR* ($I^2$ = 99.3%, 95% CIs: 98.7-99.6%). Heterogeneity in the dataset was due to variability between studies ($I^2_{study}$ = 16 %, 95% CIs: 7.21 % to 30 %), fitness components ($I^2_{fitness\:components}$ = 51.6%, 95% CIs: 22.4 to 77.6%) and taxon ($I^2_{taxon}$ = 31.7, 95% CIs: 6.97 to 62.3%).  \phantomsection

@@

The results of the meta-analysis support predictions that sexual selection **on males** can improve population fitness and accelerate adaptation [@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58]. Specifically, our results support arguments that positive genetic correlations between male mating success and female non-sexual traits are common, allowing females to benefit from a genome that has been 'purged' of deleterious alleles through selection on males [@RN94; @RN198; @RN95]. What is less clear is why sexual selection had a larger effect on female trait means and variances as opposed to males (the sex in which sexual selection is typically strongest). Below we discuss possible explanations for this result, in light of the core principle that the speed and magnitude of adaptation depends on additive genetic variance, the structure of genetic covariance, and the strength of selection [@RN317; @RN318].

@@

Although our meta-analysis revealed an overall positive effect of sexual selection, the variation in effect size across the dataset is high, as commonly is the case for studies in ecology and evolution [@RN208]. Most of the heterogeneity was explained by study and the fitness component that was measured, while the taxon, number of generations of evolution, and use of blinding showed less impact on effect size. Taxonomic diversity is limited in experimental evolution studies, which mostly use lab-suitable invertebrates with similar mating systems and sex determination. However, a meta-analysis of macroevolutionary studies on sexual selection and speciation rate found no significant taxon-based differences across a diverse sample of vertebrates and invertebrates [fish, insects, birds, spiders, reptiles, mammals; @RN165]. Despite this, taxonomic differences in the effects of sexual selection on fitness or patterns of diversity are often expected due to differences in mating systems [@RN277] and sex-determination systems [@RN262]. For example, mate choice is thought to be more prevalent in taxa with well-developed parental care [@RN196], affecting the strength and nature of sexual selection. Furthermore, male heterogametic taxa, including those commonly used in experimental evolution such as flies (Diptera), beetles (Coleoptera) and mice (Mammalia), are likely to have higher heritability of fitness from mothers to daughters. Our results -- which show greater fitness effects accruing to females -- align with this hypothesis.

@@

**Additionally, using studies that presented means, standard deviations and sample sizes (n = 352) we were able to calculate an alternative effect size: the log-response ratio (lnRR) [@Hedges_1999; @Osenberg_1997] The lnRR was used as a supplement to Hedges' g as it relaxes the assumption in equal variances between control and treatment groups (homoscedasticity).** However, lnRR was not able to be calculated from studies that

For the meta-analysis testing whether sexual selection affects phenotypic variance (as opposed to the mean), we estimated the difference in variance between each pair of treatments using the natural logarithm of the ratio between the coefficient of variation for each group (termed *lnCVR*) [@RN177]: $ln(CVfitness_{SS\ high}/CVfitness_{SS\ low})$ .**The use of _lnCVR_ allows us to determine the effects of sexual selection on phenotypic variance, with the coefficient of variation implicitly controlling for the mean-variance relationship seen in the dataset (Figure S4). As a supplement, we also calculated the natural logarithm of the absolute ratio between the absolute variation for each group (_lnVR_) in order to assess the impact of sexual selection on trait variance, irrespective of their magnitudes [@RN177].** The calculation of *lnCVR* relies on the availability of arithmetic means, standard deviations and sample sizes for the two treatment groups [@RN177; @RN190], and so we were only able to calculate *lnCVR* for 352 of 459 comparisons.  \phantomsection

@@

**Secondly, we fixed the relationship to fitness class (Ambiguous, Indirect or Direct) as a moderator variable in Bayesian and REML models (whilst maintaining study and taxon as group-level effects) to derive predictions for effect size within each of the three fitness-relationship classes, using the relevant ``predict`` functions for each of the ``R`` packages used (see below). This meta-analysis was then supplemented by another model where we fixed fitness component as a moderator variable (_e.g._, immunity, lifespan, offspring viability and female reproductive success); predictions for this model on the 22 fitness components were derived as above. Alternatively, to assess the impact of sexual selection on each fitness component independently of one another we conducted seperate meta-analyses (n = 16); subset for each fitness trait with more than three effect sizes. These models were were intercept only REML models with study and taxon as group-level effects**. Further details on model parameters can be found within the ESM.

@@

The code and data used to perform this meta-analysis is available as Electronic Supplementary Material and on Github (**link hidden for double bind review**). The repository (**link hidden for double bind review**) provides complete data tables of effect sizes, variance and sample sizes needed to reproduce our results. \phantomsection

@@

![The effect sizes used in this meta-analysis ($n$ = 459) were grouped into either direct, indirect or ambiguous measures of fitness. Overall, effect sizes were more often positive than negative. Predicted average values are presented as a diamond for each fitness-relationship category. The estimates presented here are from REML models with the grand mean across all effect sizes ($\beta$ = 0.25) shown as the blue dotted line. Predictions from both Bayesian and REML models can be found in Table S7).\label{forest_plot}](Figures/forest.plot.class.pdf)

>>>>

The grand mean for all effect sizes (**direct, indirect and ambiguous**) was positive (REML $\beta$ = 0.24, 95% CIs: 0.055 to 0.43, $p$ = 0.011; Bayesian $\beta$ = 0.25, 95% CIs: -0.0074 to 0.51, $BF_{>0}$ = 35), indicating that sexual selection **on males** typically had a net positive effect on the majority of populations and fitness components so far studied. Moreover, the effect sizes associated with the manipulation of sexual selection varied between different fitness traits. Sexual selection had a beneficial effect on most fitness traits, but varied across the three relationships to fitness \autoref{forest_plot}; \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S6}). **Sexual selection elevated fitness for traits that shared an ambiguous relationship to fitness (REML $\beta$ = 0.21, 95% CIs: 0.058 to 0.093; Bayesian $\beta$ = 0.20, 95% CIs: -0.0016 to	0.39, $BF_{>0}$ = 38, $n$ = 144) and an indirect relationship to fitness (REML $\beta$ = 0.24, 95% CIs: 0.13 to 0.36; Bayesian $\beta$ = 0.24, 95% CIs: 0.033 to 0.43, $BF_{>0}$ = 59, $n$ = 141). Additionally, sexual selection elevated fitness components directly related to fitness, albeit at a lower magnitude (REML $\beta$ = 0.13, 95% CIs: 0.019 to 0.24; Bayesian $\beta$ = 0.13, 95% CIs: -0.079 to 0.31, $BF_{>0}$ = 11, $n$ = 174). An extensive forest plot with predicted effect sizes for each fitness component is presented in Figure S1 and further detailed with model predictions and individual meta-analyses in** \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S8 and S9}. Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.42, 95% CIs: -0.64 to -0.20; Bayesian $\beta$ = -0.43, 95% CIs: -0.70 to -0.15, $BF_{>0}$ = 0.0026; $n$ = 35) and body condition (REML $\beta$ = -1.2, 95% CIs: -1.8 to -0.63; Bayesian $\beta$ = -1.2, 95% CIs: -1.9 to -0.63, $BF_{>0}$ < 0.0001, $n$ = 1).  \phantomsection

@@

The effect size estimates we recovered were highly heterogeneous **($I^2$ = 95.2%, 95% CIs: 94.4% to 95.9%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208; @Senior_I2_2016]. Heterogeneity stemmed from between-study differences ($I^2_{study}$ = 36%, 95% CIs: 26.5% to 45.4%), with variation between fitness components and taxon accounting for comparatively less heterogeneity ($I^2_{fitness\:components}$ = 0.4%, 95% CIs: 0.2% to 0.9%; $I^2_{taxon}$ = 1.4%,  95% CIs: 0.2% to 3.5%).** Variation among taxa is explored further in the ESM (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_to_just_the_higher-quality_data}{Figure S2, Table S11}).  \phantomsection

@@

As in the meta-analysis of trait means, there was high heterogeneity in the estimates of *lnCVR* ($I^2$ = 98.9%, 95% CIs: 98.7% to 99.1%). **Heterogeneity in the dataset was due to variability between studies fitness components ($I^2_{fitness\:components}$ = 12.7%, 95% CIs: 4.5% to 23.1%) and taxon ($I^2_{taxon}$ = 7.7%, 95% CIs: 1.3% to 18.4%), as well as large amounts of residual heterogeneity (78.6 %, 95 % CIs: 65.9% to 89%). Using the REML approach variance associated with the Study ID random effect was estimated at zero ($I^2_{study}$ = 0 %), however Bayesian methods suggest this value may be zero or small ($sd_{study}$ = 0.07, 95 % CIs: 0 to 0.19).**  \phantomsection

@@

The results of the meta-analysis support predictions that sexual selection **on males** can improve population fitness and accelerate adaptation [@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58]. Specifically, our results support arguments that positive genetic correlations between male mating success and female non-sexual traits are common, allowing females to benefit from a genome that has been 'purged' of deleterious alleles **through sexual selection on males** [@RN94; @RN198; @RN95]. What is less clear is why sexual selection had a larger effect on female trait means and variances as opposed to males (the sex in which sexual selection is typically strongest). **Below we discuss possible explanations for indirect fitness effects on females through sexual selection on males**, in light of the core principle that the speed and magnitude of adaptation depends on additive genetic variance, the structure of genetic covariance, and the strength of selection [@RN317; @RN318]. **However, these explanations are speculative and _post hoc_ as the result is arguably opposite to what one would predict, (*i.e.* sexual selection should have greater effects on the phenotype of males)**.

@@

Although our meta-analysis revealed an overall positive effect of sexual selection, the variation in effect size across the dataset is high, as commonly is the case for studies in ecology and evolution [@RN208]. Most of the heterogeneity was explained by study identification, while the taxon, number of generations of evolution, and use of blinding showed less impact on effect size. Taxonomic diversity is limited in experimental evolution studies, which mostly use lab-suitable invertebrates with similar mating systems and sex determination. However, a meta-analysis of macroevolutionary studies on sexual selection and speciation rate found no significant taxon-based differences across a diverse sample of vertebrates and invertebrates [fish, insects, birds, spiders, reptiles, mammals; @RN165]. Despite this, taxonomic differences in the effects of sexual selection on fitness or patterns of diversity are often expected due to differences in mating systems [@RN277] and sex-determination systems [@RN262]. For example, mate choice is thought to be more prevalent in taxa with well-developed parental care [@RN196], affecting the strength and nature of sexual selection. Furthermore, male heterogametic taxa, including those commonly used in experimental evolution such as flies (Diptera), beetles (Coleoptera) and mice (Mammalia), are likely to have higher heritability of fitness from mothers to daughters. Our results -- which show greater fitness effects accruing to females -- align with this hypothesis.

@@

**Additionally, using studies that presented means, standard deviations and sample sizes (_n_ = 352) we were able to calculate an alternative effect size: the log-response ratio (lnRR) [@Hedges_1999; @Osenberg_1997] The lnRR was used as a supplement to Hedges' g as it relaxes the assumption in equal variances between control and treatment groups (homoscedasticity).** However, lnRR was not able to be calculated from studies that

For the meta-analysis testing whether sexual selection affects phenotypic variance (as opposed to the mean), we estimated the difference in variance between each pair of treatments using the natural logarithm of the ratio between the coefficient of variation for each group (termed *lnCVR*) [@RN177]: $ln(CVfitness_{SS\ high}/CVfitness_{SS\ low})$. **The use of _lnCVR_ allows us to determine the effects of sexual selection on phenotypic variance, with the coefficient of variation implicitly controlling for the mean-variance relationship seen in the dataset (Figure S4). As a supplement, we also calculated the natural logarithm of the absolute ratio between the absolute variation for each group (_lnVR_) in order to assess the impact of sexual selection on trait variance, irrespective of their magnitudes [@RN177].** The calculation of *lnCVR* relies on the availability of arithmetic means, standard deviations and sample sizes for the two treatment groups [@RN177; @RN190], and so we were only able to calculate *lnCVR* for 354 of 459 comparisons.  \phantomsection

@@

**Secondly, we fixed the relationship to fitness class (Ambiguous, Indirect or Direct) as a moderator variable in Bayesian and REML models (whilst maintaining study and taxon as group-level effects) to derive predictions for effect size within each of the three fitness-relationship classes, using the relevant ``predict`` functions for each of the ``R`` packages used (see below). This meta-analysis was then supplemented by another model where we fixed fitness component as a moderator variable (_e.g._, immunity, lifespan, offspring viability and female reproductive success); predictions for this model on the 22 fitness components were derived as above. Alternatively, to assess the impact of sexual selection on each fitness component independently of one another we conducted seperate meta-analyses (_n_ = 16); subset for each fitness trait with more than three effect sizes. These models were were intercept only REML models with study and taxon as group-level effects**. Further details on model parameters can be found within the ESM.

@@

The code and data used to perform this meta-analysis is available as Electronic Supplementary Material and on Github (**link hidden for double blind review**). The repository (**link hidden for double blind review**) provides complete data tables of effect sizes, variance and sample sizes needed to reproduce our results. \phantomsection

@@

![The effect sizes used in this meta-analysis ($n$ = 459) were grouped into either direct, indirect or ambiguous measures of fitness. Overall, effect sizes were more often positive than negative. Predicted average values are presented as a diamond with 95 % CIs for each fitness-relationship category. The estimates presented here are from REML models with the grand mean across all effect sizes ($\beta$ = 0.25) shown as the blue dotted line. Predictions from both Bayesian and REML models can be found in Table S7).\label{forest_plot}](Figures/forest.plot.class.pdf)

### 2019-01-22 meta_analysis_sexual_selection_pop_fitness.Rmd
Changes to manuscript, I2, letter and supp Material

Using an adapted function from https://github.com/daniel1noble/metaAidR we can obtain confidence intervals for total _I^2^_ and the individual components of the random effects. There are different methods to obtain estimates of _I^2^_. Here we obtain an overall value of _I^2^_ that is weighted based on variance and where estimates of heterogeneity are sourced from sigma^2^ of the respective models. The values are based on the REML models.

```{r warning=FALSE}
I2(model.complete2, strict_dataset$var.g) %>% pander(digits = 3)
```
These values indicate that 57.4 % of total heterogeneity is due to the **between study** heterogeneity and 37.4 % for **between outcome** heterogeneity between different outcomes. The total _I^2^_  is 94.7 %, a reasonably high _I^2^_ value. However this is relatively common in Ecology and Evolution total [@Senior_I2_2016].

@@

Similar to the meta-analysis on Hedges' g we can obtain _I^2^_ for lnCVR REML model. In this case (compared to Hedges' g) we see Taxon has more of a variable effect on overall _I^2^_ estimates and the total _I^2^_ is larger.

```{r}
I2(variance.model, na.omit(strict_dataset$var.lnCVr)) %>% pander(digits = 3)
```
_________

>>>>

Using a function from https://github.com/daniel1noble/metaAidR we can obtain confidence intervals for total _I^2^_ and the individual components of the random effects. There are different methods to obtain estimates of _I^2^_. Here we obtain an overall value of _I^2^_ that is weighted based on variance and where estimates of heterogeneity are sourced from sigma^2^ of the respective models. The values are based on the REML models.

```{r warning=FALSE}
I2.model.g <- rma.mv(g, V = var.g, 
                          mods = ~ 1 + Sex * Environment, 
                          random = list(~ 1 | Observation.level, 
                                        ~ 1 | Study.ID, 
                                        ~ 1 | Outcome,
                                        ~ 1 | Taxon), 
                          method = "REML", 
                          data = strict_dataset %>% mutate(Observation.level = 1:n()))

I2(I2.model.g, strict_dataset$var.g) %>% pander(digits = 3)
```
These values indicate that 36 % of total heterogeneity is due to the **between study**. The total _I^2^_  is 95.2 %, a reasonably high _I^2^_ value. However this is relatively common in Ecology and Evolution total [@Senior_I2_2016].

@@

Similar to the meta-analysis on Hedges' g we can obtain _I^2^_ for lnCVR REML model. In this case (compared to Hedges' g) we see Taxon has more of a variable effect on overall _I^2^_ estimates and Study.ID has the variance component ($\sigma^2$) esgtimated at zero.

```{r}
I2.model.lnCVr <- rma.mv(lnCVr, V = var.lnCVr, 
                          mods = ~ 1 + Sex * Environment, 
                          random = list(~ 1 | Study.ID,
                                        ~ 1 | Outcome,
                                        ~ 1 | Taxon,
                                        ~ 1 | Observation.level), 
                          method = "REML", 
                          data = strict_dataset %>% mutate(Observation.level = 1:n()))

I2(I2.model.lnCVr, na.omit(strict_dataset$var.lnCVr)) %>% pander(digits = 3)
```

**Disclaimer**: Noticeabley, the Study.ID $I^2$ is estimated at zero with no CIs. This result is sourced from the variance component for Study.ID ($\sigma_2$) being estimated at zero with a standard error of zero. This result is questionable, thus we run the above model using ``brms`` and find the variance of the Study.ID group-level effect to be non-zero with confidence intervals including zero (see below). This is potential advantage of the Bayesian approach.

```{r}
if(!file.exists("data/I2.variance.brms.rds")){

I2.variance.brms <- brm(lnCVr| se(SE.v)  ~ 1 + Sex * Environment 
                + (1|Taxon) 
                + (1|Study.ID)
                + (1|Outcome) 
                + (1|Observation.level),
                family = "gaussian", 
                seed = 1,
                cores = 4, chains = 4, iter = 4000, 
                control = list(adapt_delta = 0.999, max_treedepth = 15),
                data = strict_dataset %>% mutate(SE.v = sqrt(var.lnCVr)) %>% mutate(Observation.level = 1:n()))
  saveRDS(I2.variance.brms, "data/I2.variance.brms.rds")

}
I2.variance.brms <- readRDS(file = "data/I2.variance.brms.rds") #Avoid re-running model above

I2.variance.brms
```
